Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project

### 2022-11-23 papers/main.tex
I think I might be done?

\begin{abstract}
    To be filled in
\end{abstract}

@@

>>>>

\begin{abstract}
    This report outlines an attempt to integrate a resource adequacy and operational security exercise. The idea is to use a unit commitment schedule which is then used as the input to a more detailed power flow model. An additional goal was to make explicit the trade-off between day ahead adequacy and real time reliability. We used an adapted version of KU Leuven's \ac{DUCPR} model which accounts for network constraints in the reserve activation phase for this purpose. However the \ac{DUCPR} model is not able to capture enough detail in the reserve activation phase for this tradeoff to be made. This and other omissions of the \ac{DUCPR} model when compared to the power flow model meant the results of the two models differed significantly.
\end{abstract}

@@

\section{Thoughts}
